\section{Weight and Mass}
	Definition: Weight is the force on an object due to gravity. It depends on the local gravitacional strength.

	Definition: Mass is the measure of the amount of matter in an object. It is the same everywhere.

	Definition: Mass is the measure of an object's inertia, which is its inherint resistance to being accelerated.

	\begin{align}
		\vec{F_{g}} = \ &\text{force of gravity}& \notag \\
		m = \ &\text{mass}& \notag \\
		\vec{g} = \ &\text{acceleration due to gravity}& \notag \\
		\vec{F_{g}} = \ &m\vec{g}& \notag
	\end{align}

	\begin{align}
		&\text{Units}& &\text{Mass}& &\text{Force/Weight}& \notag \\
		&\text{Metric}& &kg = \text{kilogram}& &1 N = 1 \text{Newton} = 1 kg*m/s^{2}& \notag \\
		&\text{English}& &sl = \text{slug}& &1 lb = 1 \text{pound} = 1 sl*ft/s^{2}& \notag
	\end{align}

	Example: What is weight on Earth of $1 kg$?

	\begin{align}
		F_{g} = \ &mg& \notag \\
		= \ &(1 \ kg)(9.8 \ m/s^{2})& \notag \\
		= \ &9.8 \ kg*m/s^{2}& \notag \\
		= \ &9.8 \ N& \notag
	\end{align}

	The English weight on Earth of $1 \ kg$ is $\approx 2.2 \ lb$. So $9.8 \ N \approx 2.2 \ lb$.

	Example: Doctor J. weighs $162 \ lb$ on Earth. What is his mass?

	\begin{align}
		F_{g} = \ &mg& \notag \\
		162 \ lb = \ &m(32.2 \ ft/s^{2})& \notag \\
		m = \ &\frac{162 \ lb}{32.2 ft/s^{2}} = 5.03 \ sl& \notag
	\end{align}

\section{Newton's 2nd Law}
	\begin{align}
		\vec{F_{net}} = m\vec{a} \notag
	\end{align}
	Where
	\begin{align}
		\vec{F_{net}} = \ &\sum \vec{F} = \text{sum of all forces on an object}& \notag
	\end{align}
	\begin{align}
		\vec{a} = \ &\frac{\vec{F_{net}}}{m}& \notag
	\end{align}

	Example: A $3 \ kg$ mass accelerates at $2 \ m/s^{2}$. What is net force?

	\begin{align}
		\vec{F_{net}} = \ &ma& = \ &(3 \ kg)(2 \ m/s^{2}) = 6 kg*m/s^{2} = 6 N& \notag
	\end{align}

	Example: An $18 \ lb$ net force causes a cart to speed at steadily from $10 \ ft/s$ to $16 \ ft/s$ in $2.0 \ s$ What does cart weigh?

	\begin{align}
		a = \ &\frac{v - v_{0}}{t} = \frac{(16 \ ft/s) - (10 \ ft/s)}{2.0 \ s}& \notag \\
		= \ &\frac{6 \ ft/s}{2.0 \ s}& \notag \\
		= \ &3 \ ft/s^{2}& \notag
	\end{align}

	\begin{align}
		F_{net} = \ &ma& \notag \\
		m = \ &\frac{F_{net}}{a} = \frac{18 \ lb}{3 \ ft/s^{2}}& \notag \\
		= \ &6 \ sl& \notag
	\end{align}

	\begin{align}
		F_{g} = \ &mg& \notag \\
		= \ &(6 \ sl)(32.2 \ ft/s^{2})& \notag \\
		= \ &193.2 sl*ft/s^{2} = 193.2 \ lb& \notag
	\end{align}
